Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-06-30 paper/Draft.tex
Finalized first drafting. Figure table notes. Forecsting efficiency literature needs to be added.landscape tables. Titles of figures.

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variable that are not available until recent provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.

@@

	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade. This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing theories empirically.  On one hand, various theories built upon different micro foundations produce some similar macro patterns. For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.  On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.

	This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probabilistic forecast from both professional forecasters survey and household survey. Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models. But in the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.

	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of variables of the forecast. .\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.} With density forecasts. the variance of individual forecast can be estimated as an indicator of the uncertainty. Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency. Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions.

	This paper is related to three strands of literature. First, recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data. For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. More recent examples include \citet{coibion2018firms} on firms' managers. In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}, In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demografics and macroeconomic experiences they have had. For instance, \citet{malmendier2015learning}. However, all of these research simply rely upon point forecsts instead of densitity forecast or surveyed uncertainty. This is one theme on which that this paper differs from the existing literature.

@@

	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probiblistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{xx}, \citet{xx} have all shown that this is actually less of a concern. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses. Broadly speaking, the advocators have argued that going beyond revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty.

@@

	$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instantaneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. Examples of such include multi-prior or model uncertainty. \citet{xx}. }

@@

	The population analogues of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents. Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively. Hereafter, they are termed as population mean forecast, population uncertainty and population forecast error, respectively. In addition, disagreements is defined as the cross-sectional variance of mean forecasts of individual agents.  Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $. To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.  \footnote{This is the same terminology used by \citet{xx}.}

@@

	Overal the results derived in coming sections are  not sensitive to if the shock is serially correlated. Also, it allows for the possibility of time varying volatility, i.e. the variance of $\omega$ is thus $\sigma^2_{t,\omega}$ with time subsript.

@@

	As the forecaster approaches $t+h$ ($k$ approaches to $h$), there is an unambiguous reduction in uncertainty (or efficiency gain in the forecating literature) as more and more shocks have realized.Equivalently, revision is always negative and should be exactly equal to the variance of the realized shocks according to FIRE.

@@

	Another simple prediction is that both disagreements and uncertainty do not respond to realized shocks any any point of the time.

@@

	The theory of sticky expectation (\citet{mankiw2002sticky}, \citet{carroll2003macroeconomic} etc.), regardless of various ways micro-foundations, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One tractable assumption is that there is a homogenous Poisson rate $\lambda$ of updating among the population. Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

@@

	It is easy to show that the average forecast errors are serially correlated(Equation \ref{FESEPop}). For checking, setting $\lambda=1$, then the SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully respond to newly realized shocks at time $t$.

@@

	 Similarly, the inefficiency of reducing uncertainty in SE take the following form in aggregate level. Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.

@@

	\begin{itemize}
		\item Population mean forecast partially responds to shocks and with lags. 
		\item Forecast errors are serially correlated. 
		\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
		\item Population average uncertainty revision underreacts to volatility of the shocks.
	\end{itemize}

@@

	where the Kalman gain is a $P$ of size of two that determines the degrees of reaction to signals.

@@

	A comparable parameter with $1-\lambda$ in SE that governs rigidity in NI is $1-PH$. It is a function of previous period uncertainty about $y_t$ and noisiness of the signals determined by $\Sigma^v$. Note $P$ is time variant as the variance is updated by the agent each period. The time varying nature of rigidty will be dicussed later. For now, I drop time $t$ from $P$ to avoid clusterring.

	The underreaction to news generate serial correlation of forecast errors with the coefficient being $\rho^2(1-PH)$. it does not only depend on $PH$, but also the forecast horizon $h$. As $\rho<1$, the rigidity declines with longer horizon. In this regard, the rigidity implied by NI and SE are different because the form is fixed and the later is horizon dependent.

@@

	Kalman filtering updates the variance according to normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in previous period and variance of signals.

@@

    This directly gives the revision in uncertainty from time $t-1$ to $t$. The newly arrived information, although noisy, still brings aobut information gains, thus leading to an unambiguously drop on uncertainty. But due to the signal is not perfect, i.e. $\Sigma^v \neq 0$, there is inefficiency in reducing uncertainty compared to FIRE.

@@

	In order to be directly comparable with the revision in uncertainty in FIRE (Equation \ref{VarREPopRv}) and SE (Equation \ref{VarSERv}), the nowcasting uncertainty about $y_t$ needs to be converted to $h$-period-ahead forecating uncertainty. This is simply to add the discounted nowcasting uncertainty by $\rho^{2h}$ to the uncertainty about future unrealized shocks.

@@

	Figure \ref{IllustrateNI} illustrates the Kalman filtering problem over the $10$ period horizon from to $t$ to $t+10$  following one-time shock of one standard deviation $\omega_t$.  For illustration purpose, I assume that both private and public signals have the equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e. $\frac{\sigma^2_\omega}{1-\rho}$.  A particular draw of public and private signals their respetive conditional distributions of given $y_t$ are plotted.

	From the top left figure, the agent's nowcasting $y_{t+k|t+k}$, namely her best real-time guess based on prior and the realized signal at each period ranghly tracks the $y_{t+k}$ and responds partially to signals in each period. Correspondingly, her forecating of $y$ at $t+10$ also centers around the true value.

	FIRE implies agent learns realized $y$ in each period perfectly. Thus the nowcasting remains zero thoughout the whole horizon. Nowcasting uncertainty picks up in the realization of shock and gradully declines as more and more informaiton signals are realized. This comes from the information gains from Kalman filtering.

    The sharp rise in nowcasting uncertainty in the begining of the period is only humbly reflected in the forecasting uncertainty seems counter intuitive in the first sight. Actually this is due to nowcasing uncertainty is discounted by the factor of $\rho^2(h-k)$.  (Equation \ref{VarNIEq}). It is also interesing that for the particular configurations of noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may expected compared to FIRE.  This has important quantitative implications for NI models. In particular, the nosiness of the signals need to be consistent with the degree of rigidity. I will return this point in the next section.

@@

	The implications for disagreements are straightfoward. First, the disagreements decreases with the forecast horizon for the reason of discounting. Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.

@@

	Taking stock, both SE and NI predict rigidity in expectation incorporating arrival of new information. In the former context, the rigidity comes from the simple non-updating of the most realization of the variable. In the later case, the rigidity comes from a partial reaction to new information due to its nosiness.  In addition to forecast and disagreements, the rigidity is also reflected in the dynamics of uncertainty.

	According to FIRE, the revision in uncertainty from $t-1$ to $t$ is eactly equal to  the variance of the shock that is realized at time $t$. Taking $h=1$ as a simple and plug it in Equation \ref{VarREPop}, we have

	\begin{eqnarray}\label{VarREPopRv1}
	\bar \sigma^{*2}(y_{t+1}|t) - \bar \sigma^{*2}(y_{t+1}|t-1) = - \rho^2\sigma^2_\omega
	\end{eqnarray}

	In SE, the one-period revision in uncertainty is less due the non-npdate of population.

	\begin{eqnarray}\label{VarSEPopRv1}
     \bar \sigma^{2}(y_{t+1}|t) - \bar \sigma^{2}(y_{t+1}|t-1) = (1-\lambda) - \rho^2\sigma^2_\omega
    \end{eqnarray}

	Figure \ref{ir_pop} illustrats the impulse response of population moments to a hypothetical one-time shock at time $t$ according to different theories.

	on the dynamics of revision as one approaches the terminate date, i.e. forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e. $y_{t+h}$,$y_{t+h+1}$.

	This is the most intuitively seen in the dynamics of uncertainty. In particular, as one approach the realization $t+h$, uncertainty necessarily drop for FIRE and attains zero at the last period.

@@

	One of the common predictions of SE and NI is there is information rigidity or stickiness of expectations.  But both theories have subtle difference in implied rigidity. I illustrate this in Figure \ref{rigidity}. One notable difference is that SE's rigidity is exogenously fixed. NI's rigidity is endogenously determined by the noisiness of the signals and it is time varying.

@@

	\subsection{Discussion of other theories}

	\begin{enumerate}
		\item Rational inattention. 
		\begin{itemize}
			\item Chris Sim's model.\citet{sims2003implications} Information serves the role of uncertainty reduction measured by relative entropy. Agents optimally trade off the fixed cost of being attentative versus the gain from uncertainty gain.   
			\item Ricardo Reis's model. \citet{reis2006inattentive}
			\item Xavier Gabaix's sparse matrix model. \citet{gabaix2014sparsity}
		\end{itemize}

		\item Epidemiological view. \citet{carroll2003macroeconomic} Regardless of the micro-foundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.

		\item Strategic behaviors. Second order belief, i.e., what you believe of what others believe. \citet{angeletos2009incomplete}

	\end{enumerate}

@@

	Professional Forecasters(SPF) and New York Fed Survey of Consumer Expectation(SCE).

	The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both current year forecast and 1-year-ahead inflation forecast each quarter.

	SCE data, although each individual is surveyed for 12 months in a row, is only asked to forecast 1-year-ahead inflation. This is especially so in the density forecast. So we can only perform a weak test.

	We follow \citet{engelberg2009comparing} to estimates the density distribution of each individual surveyee for SPF. New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty. Therefore, I directly use them.

	For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.   For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extreme values. \footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}

	A summary of the data information is as below.

@@

	\section{Shock-based tests of expectation rigidity }\label{IRShocks}

@@

	It is widely documented in the literature that behaviors of households expectations more idiosyncratic in comparison with that of professional forecasters. \footnote{For this reason, \cite{carroll2003macroeconomic}, for instance, use median professional forecasts as to approximate ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.  The monthly data of SCE allows an analysis in a higher frequency but for a shorter period 2013-2019.

@@

	\section{Conclusion}

>>>>

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variable that are not available until recent provide one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.

@@

	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade. This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing these theories empirically.  On one hand, various theories built upon different micro foundations produce somewhat similar macro patterns. For instance, the notion of expectation rigidity micro-founded by different theories mostly generate sluggish response to new information.  On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.

	This paper extends this research effort by bringing an additional moment of forecasts into perspective, i.e. uncertainty. Specifically, in this paper I first derive the testable predictions from various theories on uncertainty and carefully compare the differences mostly obvious seen from uncertainty. Second empirically I test and estimate these implications utilizing the recently available probabilistic forecasts from both professional forecasters survey and household survey. Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models. In the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.

	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of values of the variable of forecast\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.}. With density forecasts,  variance of individual forecast can be estimated as an indicator of the uncertainty. Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency. Besides, the dispersion of uncertainty across agents, and its relationship with other moments widely looked by the literature, such as forecast errors and disagreements provide many insights as to how the agents expectation actually work.

	This paper is related to three strands of literature. First, recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data. For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. More recent examples include \citet{coibion2018firms} on firms' managers. In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demographics and macroeconomic history experienced(\citet{malmendier2015learning}, \citet{das2017socioeconomic},etc.). In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}.  However, all of these research simply rely upon point forecasts instead of density forecast or surveyed uncertainty. This is one theme on which this paper differs from the existing literature.

@@

	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probiblistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people}and other work have all shown that this is actually less of a concern. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses. Broadly speaking, the advocators have argued that going beyond revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty.

@@

	$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instantaneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. Examples of such include multi-prior or model uncertainty. \citet{hansen2001robust}, \citet{hansen2008robustness}, etc.}

@@

	The population analogues of individual mean forecast, uncertainty and forecast errors are simply the average of the individual moments taken across agents. Denote them as $\bar y_{t+h|t}$, $\bar \sigma^2_{t+h|t}$, and $\overline{FE}_{t+h|t}$, respectively. Hereafter, they are termed as population mean forecast, population uncertainty and population forecast error, respectively. In addition, disagreements is defined as the cross-sectional variance of mean forecasts of individual agents.  Denote it as $\overline{Var}_{t+h|t}(y_{i,t+h|t}) $. To simplify notation, let us directly call it $\overline{Disg}_{t+h|t}$.

@@

	Although we make the assumption of i.i.d. shock here. The framework allows for the possibility of time-varying volatility, i.e. the variance of $\omega_t$ is thus $\sigma^2_{t,\omega}$ with time subsript.

@@

	As the forecaster approaches $t+h$ ($k$ approaches to $h$), there is an unambiguous reduction in uncertainty (or efficiency gain in the forecasting literature) as more and more shocks have realized. Equivalently, revision is always negative and should be exactly equal to the variance of the realized shocks according to FIRE.

@@

	Another simple result is that both disagreements and uncertainty do not respond to realized shocks any any point of the time. But this does not differentiate FIRE from other models.

@@

	The theory of sticky expectation (\citet{mankiw2002sticky}, \citet{carroll2003macroeconomic} etc.), regardless of various micro-foundations, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One tractable assumption is that there is a homogenous Poisson rate $\lambda$ of updating among the population. Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

@@

	It is easy to show that the average forecast errors are serially correlated(Equation \ref{FESEPop}). For double checking, setting $\lambda=1$, SE collapses to FIRE, in which there is no serial correlation between forecast errors and it fully responds to newly realized shocks at time $t$.

@@

	Similarly, the inefficiency of reducing uncertainty in SE takes the following form in aggregate level. Average uncertainty at any point of time is now a weighted average of uncertainty to agents whose last updates have taken place in different periods of past.

@@

	\begin{itemize}
		\item Population mean forecast partially responds to shocks and with lags. 
		\item Forecast errors are serially correlated. 
		\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
		\item Population average uncertainty revision under-reacts volatility of the shocks.
	\end{itemize}

@@

	where the Kalman gain $P$ is a vector of size of two that determines the degrees of reaction to signals.

@@

	A comparable parameter with $1-\lambda$ in SE that governs rigidity in NI is $1-PH$. It is a function of previous period uncertainty about $y_t$ and noisiness of the signals determined by $\Sigma^v$. Note $P$ is time variant as the variance is updated by the agent each period. The time varying nature of rigidity will be discussed later. For now, I drop time $t$ from $P$ to avoid clustering.

	The under-reaction to news generate serial correlation of forecast errors with the coefficient being $\rho^2(1-PH)$. it does not only depend on $PH$, but also the forecast horizon $h$. As $\rho<1$, the rigidity declines with longer horizon. In this regard, the rigidity implied by NI and SE are different because the form is fixed and the later is horizon dependent.

@@

	Kalman filtering also updates the variance according to rule normal updating.   The posterior variance at time $t$ is a linear function of uncertainty in previous period and variance of signals.

@@

	This directly gives the revision in uncertainty from time $t-1$ to $t$. The newly arrived information, although noisy, still brings about information gains, thus leading to an unambiguously drop on uncertainty. But due to the signal is not perfect, i.e. $\Sigma^v \neq 0$, there is inefficiency in reducing uncertainty compared to FIRE. This mea

@@

	In order to be directly comparable with the revision in uncertainty in FIRE (Equation \ref{VarREPopRv}) and SE (Equation \ref{VarSERv}), the nowcasting uncertainty about $y_t$ needs to be converted to $h$-period-ahead forecasting uncertainty. This is simply to add the nowcasting uncertainty discounted by $\rho^{2h}$ to the uncertainty about future unrealized shocks.

@@

	Figure \ref{IllustrateNI} illustrates the Kalman filtering problem over the $10$ period horizon from to $t$ to $t+10$  following one-time shock of one standard deviation $\omega_t$.  For illustration purpose, I assume that both private and public signals have the equal degree of noisiness and their standard deviation is equal to the unconditional standard deviation of $y$, i.e. $\sqrt{\frac{\sigma^2_\omega}{1-\rho^2}}$.  A particular draw of public and private signals from their respective conditional distributions given $y_t$ are plotted.

	From the top left figure, the agent's nowcasting $y_{t+k|t+k}$, namely her best real-time guess based on prior and the realized signal at each period roughly tracks the $y_{t+k}$ and responds partially to signals in each period. Correspondingly, her forecasting of $y$ at $t+10$ also centers around the true value.

	FIRE implies agent learns realized $y$ in each period perfectly. Thus the nowcasting remains zero throughout the whole horizon. Nowcasting uncertainty picks up in the realization of shock and gradually declines as more and more information signals are realized. This comes from the information gains from Kalman filtering.

	The sharp rise in nowcasting uncertainty in the beginning of the period is only humbly reflected in the forecasting uncertainty seems counterintuitive in the first sight. Actually this is due to nowcasting uncertainty is discounted by the factor of $\rho^2(h-k)$.  (Equation \ref{VarNIEq}). It is also interesting that for the particular configurations of noisiness of the signals, the drop in forecasting uncertainty from NI is not as inefficient as one may have expected compared to FIRE.  This has important quantitative implications for NI models. In particular, the nosiness of the signals need to be consistent with the degree of rigidity. I will return this point in the next section.

@@

	The implications for disagreements are straightforward. First, the disagreements decreases with the forecast horizon for the reason of discounting. Second, the disagreements depends on noisiness private signals, but not on that of public signals and the variance of the true variable $y$. Third, similar to SE, the disagreements also increase with the rigidity parameter $P$ in this model.

@@

	Taking stock, both SE and NI predict rigidity in expectation incorporating arrival of new information. In the former context, the rigidity comes from the simple non-updating of the most realization of the variable. In the later case, the rigidity comes from a partial reaction to new information due to its nosiness.  In addition to forecast and disagreements, the rigidity is also reflected in the dynamics of uncertainty.  Uncertainty in SE does not resolve as rapid as in FIRE because the newly realized shocks do not get updated by some of the agents. While in NI, the drop in uncertainty is dampened because the there is positive uncertainty associated with the real-time realization of the variable.

	Figure \ref{ir_pop} illustrates the impulse response of population moments to a hypothetical one-time shock of size one unit at time $t$ according to different theories. Still, I maintain the assumption in \ref{IllustrateNI} that the standard deviation of private and public signals are both equal to the one unconditional standard deviation of $y$.  And the $\lambda$ is set to be $0.25$, implying on average an update interval of four quarters.

	Both FE and disagreements from SE and NI exhibit sluggish adjustment following the shock as we have anticipated. Both pick up in the time of the shock and gradually declines over the horizon as the forecaster approaches terminate date $t+10$. The difference is that in NI, both the forecast and forecast errors move up and downs around the the smooth version of the SE since noise is not perfect.

	The dynamic of disagreements and uncertainty, however,  illustrate one parametric differences between SE and NI. In particular,  the initial pick in disagreements is higher for NI compared to SE for the particular parameter values. This implies that the noise of the private signal that drives the disagreements in NI exceeds that the extent to which the agents do not simultaneously update in SE. \footnote{Another subtle point is that if the disagreements jump the highest in the time of the shock turns out depend on value of $\lambda$. In the fixed horizon forecasting, $\lambda=0.5$ is the maximizer of disagreements.}

	For the same parameters, however, the inefficiency seen in dynamics of uncertainty seem to be way more substantial for SE than in NI. Overall, the uncertainty drops almost as efficiently as in FIRE. The difference of SE and the FIRE benchmark is more notable. This is the graphical illustration of Equation \ref{VarSERv}.

@@

	In order to understand why the rigidity seen from uncertainty is de facto much lower in NI that in SE for a sensible values of the noisiness of signals , I plot the implied rigidity from two models in Figure \ref{rigidity} for three different values of nosiness of signals in NI while fixing rigidity in SE to be $1-\lambda =0.75$. In particular, the noisiness range from $0.1$, $1$ and $10$ times of the long-run variance of $y$.

	As it is made clear by the Figure, one notable difference of the two models is that SE's rigidity is exogenously fixed while NI's rigidity is endogenously determined by the horizon thus time varying. In particular, the implied rigidity from NI in the time of the shock, given there is substantial information gain from Kalman filtering in the same period, is quite low. For a noisiness of both signals as 10 times as high of the unconditional standard deviation of $y$, the rigidity only reaches the fixed rigidity in SE till the 8-th period. But since by that time, the initial information provided by the shock at time $t$ has been mostly absorbed by NI agent, so in fact the uncertainty revision in NI is quite efficient compared to SE models.  This echoes our earlier observation in Figure \ref{IllustrateNI}.

@@

	In summary, although NI and SE both predict the similar qualitative predictions of rigidity when it comes the behavior of FE and disagreements, de facto, the efficiency of forecasting from NI is higher than SE. The only additional uncertainty in NI to that FIRE is the nowcasting uncertainty, which is discounted in future. While in SE, the uncertainty do come from the lagged update of information, which involve all uncertainty of the shocks that are not yet updated in agents' information set.

@@

	The focus of this paper naturally restricts my options of the survey data to use compared to other empirical  literature of testing theories of expectation formation.  The surveys who have elicited density forecasts of macroeconomic variables for a sufficiently long period has been rare. More rare, for the purpose of the paper, is the data structure that allows for compare the revisions across vintages of forecasts that have a terminate date of realization, either in individual level or aggregate level.

	Professional Forecasters(SPF)  meet the both criteria thanks to the density forecasts of a number of macroeconomic variables, including headline CPI and PCE inflation they have started eliciting since 2007. In particular, the density forecasts are both made for current year forecast, basically nowcasting, as well as one-year-ahead forecast. This allows for directly testing the implications from the revisions in uncertainty.

	The New York Fed Survey of Consumer Expectation(SCE) that started in 2013 has at least met the first criteria. In particular, households are asked to provide their perceived probabilities to 1-year-ahead inflation for a range of values. \footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one. NY Fed stuff has excluded those who do not meet this criteria.} The high-frequency monthly panel structure also provides an invaluable chance to explore the dynamics of uncertainty. Around one third of the households are surveyed for 12 months.

	I follow \citet{engelberg2009comparing} to estimate the density distribution of each individual surveyee for SPF. This is the same approach adopted by New York Fed stuff \citet{armantier2017overview} has followed the same procedures for SCE and directly provided their estimate of uncertainty. I directly use them.

	Unsurprisingly, both surveys need some  winsorization. For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentile as these are typically abnormals that are due to measurement errors or other reasons.   For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extreme values. All the results in this paper are robust to a different thresholds such as 10 and 1 percentile. \footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}

	A summary of the data information is in Table \ref{DataInfo}.

@@

	\section{Shock-based tests of expectation rigidity }\label{ShockBased}

@@

	It is widely documented in the literature that behaviors of households expectations more idiosyncratic in comparison with that of professional forecasters. \footnote{\cite{carroll2003macroeconomic}, for instance, uses median professional forecasts as an approximate of the ``rational'' forecasts.} This section extends the impulse responses estimation of externally identified shocks to the household forecasts moments of SCE.  The monthly data of SCE allows an analysis in a higher frequency but for a shorter period 2013-2019.

@@

	\section{Conclusion}\label{Conclusion}
